Ecuador plant species GIFT data

### 2023-01-22 code/L0/L0_Ecuador_plants_GIFT.Rmd
retrive data for Ecuador get checklist get richness and trait coverage = 0

# Load required packages
```{r}
remotes::install_github("https://github.com/BioGeoMacro/GIFT",
dependencies = TRUE)
library(GIFT)
library(mde)
library(DataExplorer)
library(summarytools)
```

# Get data for Ecuador from GIFT database

>>>>

# Load required packages
```{r}
#run first time only
#remotes::install_github("https://github.com/BioGeoMacro/GIFT",dependencies = TRUE)
library(GIFT)
library(mde)
library(DataExplorer)
library(summarytools)
```

# Get data for Ecuador from GIFT database
```{r}
# retrive entity_ID for Ecuador
regions <- GIFT_regions()
str(regions)
regions[regions$geo_entity %in% "Ecuador",]

```

```{r}
Ecuador_shape <- GIFT_shape(entity_ID = 10348)
```

```{r}
GIFT_data <- GIFT_checklist(floristic_group = 'all', geo_type = 'All', shp = Ecuador_shape, overlap = 'extent_intersect', taxonomic_group = TRUE)
```

```{r}
richness <- GIFT_richness(what = "species_richness")
trait_coverage <- GIFT_richness(what = "trait_coverage")
```

```{r}
richness[richness$geo_entity %in% 10348,]
trait_coverage[trait_coverage$geo_entity %in% 10348,]
```

```{r}

```
